\hlavicka{Hotel California}{Eagles}

\HmiSiroky{} \FisSiroky{} \ASiroky{} \ESiroky{} \GSiroky{} \DSiroky{} \EmiSiroky{} \FisSiroky{} 

\sloka{
\Hmi On a dark desert highway,\\
\Fis Cool wind in my hair, \\
\A Warm smell of colitas \\
\E rising up through the air.\\ 
\G Up a head in the distance, \\
I \D saw a shimmering light \\
My \Emi head grew heavy and my sight grew dim,\\ 
I \Fis had to stop for the night \\
}
\sloka{
There she stood in the doorway \\
I heard the mission bell \\
And I was thinking to myself\\ 
this could be heaven or this could be hell \\
Then she lit up a candle \\
And she showed me the way \\
There were voices down the coridor \\
I thought I heard them say: \\
}
\refren{
\G Welcome to the Hotel Cali\D fornia.\\ 
Such a \Emi lovely place (such a lovely place)\\ 
such a \HmiSedm lovely face. \\
\G Plenty of room at the Hotel \D California.\\ 
Any \Emi time of year (any time of year) \\
you can \Fis find it here. \\
}
\begin{multicols}{2}
\sloka{
\Hmi Her mind is Tiffany twisted, \\
\Fis she got a Mercedes Benz, \\
\A she got a lot of pretty, pretty boys\\
\E that she calls friends,\\ 
\G How they dance in the courtyard \\
\D sweet summer sweat. \\
\Emi Some dance to remember\\ 
\Fis some dance to forget. \\
}
\sloka{
So I called up the captain: \\
Please bring me more wine \\
We haven't had that spirit \\
here since nineteen sixtynine.\\ 
And still those voices are calling from far away \\
wake you up in the middle of the night \\
just to hear them say: \\
}
\refren{
Welcome to the Hotel California. \\
Such a lovely place (such a lovely place) \\
such a lovely face. \\
They livin'it up at the Hotel California. \\
What a nice surprice (what a nice surprise) \\
bring your alibis.  \\
}
\sloka{
Mirrors on the ceiling, \\
The pink champagne on ice, (and she said,) \\
We are all just prisoners here of our own device.\\
And in the master's chambers \\
They gathered for the feast, \\
They stab it with their steely knives,\\ 
but they can't kill the beast. \\
}
\sloka{
Last thing I remember, \\
I was running for the door\\ 
I had to find the passage \\
back to the place I was before.\\ 
Relax, said the night man \\
We are programed to receive, \\
You can check out any time you like,\\ 
but you can never leave. \\
}
\end{multicols}
